Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-20 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:19	16:08:56	(Wed19.Aug)
la2pdf commit - 2015:08:20	15:01:26	(Thu20.Aug)

The LCA beamformer interates through a set of $P$ windows and $p$ that yields the least output power:
%
\begin{align}
\underset{p}{\argmin}\, E\{|z[n]|^2\} = \underset{p}{\argmin}\, E\big\{|\w_{\beta,\phi}\H\x[n]|^2\big\}\\
\qquad\text{subject to}\qquad \w\H\a = 1
\end{align}\label{lca_criterion}
%
We can estimate $E\big\{|\w_p\H\x[n]|^2\big\}$ as
%
\begin{align*}
\sigma^2_{z_p}[n] = \frac{1}{N_k} \sumb{n'=n-K}{n+K} | z_p[n'] |^2
\end{align*}
%
To add some extra flexibility, we can also estimate the variance by a weighted combination of local pixels
%
\begin{align*}
\sigma^2_{z_p}[x,n] = \frac{1}{N_x N_k} \sumb{x'=x-X}{x+X} \sumb{n=n-K}{n+K} w_\text{prf}[x',n']\big| z_p[x',n'] \big|^2
\end{align*}
%
where $w_\text{prf}[x',n']$ is a normalized 2 dimensional weight function.

@@

\section{Kaiser windows}\label{kaiser_windows}

@@

\begin{align}
\w_{\beta,\phi} = \f_\beta\H\diag{(\a_\phi)}\\
\end{align}
%
where
%
\begin{align}
\a_\phi = \bmat{
1 \\
e^{-j\frac{md}{\lambda}\sin(\phi)} \\
\vdots\\
e^{-j\frac{(M-1)d}{\lambda}\sin(\phi)}
}
\end{align}

Before we apply the window to the sensor data, we normalize it to ensure unit gain in the direction of interest:
%
\begin{align}
\w = \frac{\vec f}{\f\T\1} \quad\quad\text{where}\quad\quad \f =
\bmat{
f_0 \\ \vdots \\ f_{M-1}                                                           
}
\end{align}
%
Note that the normalization factor $\f\T\1$ is the reciprocal of the window's coherent gain. Since the signal-to-noise gain is constant for a given window, this normalization also proportionally increases the  incoherent noise gain.

\begin{align}
\w = \frac{\a\f}{\f\T\a} = 
\end{align}

>>>>

The LCA beamformer interates through a set of $P$ windows and $p$ that yields the least output power:
%
\begin{align}
\underset{p}{\argmin}\, E\{|z[n]|^2\} = \underset{p}{\argmin}\, E\big\{|\w_{\beta,\phi}\H\x[n]|^2\big\}\\
\qquad\text{subject to}\qquad \w\H\a = 1\label{eq_lca_constraint}
\end{align}\label{lca_criterion}
%
We can estimate $E\big\{|\w_p\H\x[n]|^2\big\}$ as
%
\begin{align*}
\sigma^2_{z_p}[n] = \frac{1}{N_k} \sumb{n'=n-K}{n+K} | z_p[n'] |^2
\end{align*}
%
To add some extra flexibility, we can also estimate the variance by a weighted combination of local pixels
%
\begin{align*}
\sigma^2_{z_p}[x,n] = \frac{1}{N_x N_k} \sumb{x'=x-X}{x+X} \sumb{n=n-K}{n+K} w_\text{prf}[x',n']\big| z_p[x',n'] \big|^2
\end{align*}
%
where $w_\text{prf}[x',n']$ is a normalized 2 dimensional weight function.

@@

\subsection{Window function: Kaiser}\label{kaiser_windows}

@@

To allow LCA some added flexibility we also create variations of each window that are steered a little to each side.
%
\begin{align}
\w_{\beta,\phi} = \frac{\f_\beta\H\diag{(\a_\phi)}}{\f_\beta\H\a_\phi}\\
\end{align}
%
where
%
\begin{align}
\a_\phi = \bmat{
1 \\
e^{-j\frac{md}{\lambda}\sin(\phi)} \\
\vdots\\
e^{-j\frac{(M-1)d}{\lambda}\sin(\phi)}
}.
\end{align}
%
Here $d$ is the element spacing and $\lambda$ is the wavelength. The normalization factor $\f_\beta\H\a_\phi$ is the reciprocal of the window's coherent gain. It is needed to ensures unit gain in the direction of interest as required by (\ref{eq_lca_constraint}). Since the signal-to-noise gain is constant for a given window, this normalization also proportionally increases the  incoherent noise gain.
